---
title: "K estimation paper analysis and figures"
author: "Kate Stankiewicz"
date: "3/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### load libraries and set wd ###

```{r}
library(dplyr)
library(tools)
library(tidyverse)
library(reshape)
library(plotrix)
library(tidyr)
library(ggplot2)
library(cowplot)
library(adegenet)
library(poppr)
library(hierfstat)
library(ggpattern)
```

# focused Section #
## Loop to read in each dataset ##

```{r}
setwd("~/focused/all_estimate_files")

ldf <- list() 
listcsv <- dir(pattern = "*.csv") 
for (k in 1:length(listcsv)){
 ldf[[k]] <- read.csv(file = listcsv[k], check.names = F, row.names = 1, header = T)
}
names(ldf) <- gsub(".csv","",
                       dir(pattern = "*.csv"),
                       fixed = TRUE)
names(ldf) <- gsub("Results_Estimators_","", names(ldf), fixed = TRUE)
names(ldf) <- gsub("_run","", names(ldf), fixed = TRUE)
```

## process each dataset ##

```{r}
# get only the estimators you want
ldf_est_only <- lapply(ldf, function(x) x <- x[-c(3:15), ])

# create a new column with k values
ldf_k_vals <- lapply(ldf_est_only, function(x) cbind(x, k_val = colnames(x)[apply(x,1,which.max)]))

#keep only the K values
ldf_k_vals_only <- lapply(ldf_k_vals, function(x) x[c('k_val')])

#transpose each
t_ldf_k_vals_only <- lapply(ldf_k_vals_only, function(x) as.data.frame(t(x)))

#convert to one big dataframe
one_df <- do.call(rbind, t_ldf_k_vals_only)

#make only numeric
one_df[] <- lapply(one_df, gsub, pattern= "K=", replacement = "")
one_df_num <- as.data.frame(sapply(one_df, as.numeric))
rownames(one_df_num) <- rownames(one_df)
```

## get differences from deltaK and ln Pr(X|K)) ##

```{r}
#for deltaK
dk_diff <- one_df_num[,c(1,3:ncol(one_df_num))]
dk_diff[2:ncol(dk_diff)] <- dk_diff[2:ncol(dk_diff)]-dk_diff[,1]
dk_diff <- dk_diff[,2:ncol(dk_diff)]

#for ln Pr(X|K))
lnk_diff <- one_df_num[,2:ncol(one_df_num)]
lnk_diff[2:ncol(lnk_diff)] <- lnk_diff[2:ncol(lnk_diff)]-lnk_diff[,1]
lnk_diff <- lnk_diff[,2:ncol(lnk_diff)]
```


## get summary stats for DeltaK ##

```{r}
#get the means
means_dk <- as.data.frame(colMeans(dk_diff))
colnames(means_dk) <- c("mean")
means_dk$estimator <- rownames(means_dk)

#get the sd
sd_dk <-sapply(dk_diff, sd)
sd_dk <- as.data.frame(sd_dk)
colnames(sd_dk) <- c("sd")
sd_dk$estimator <- rownames(sd_dk)

#get SEM
SEM_dk <- sapply(dk_diff, std.error)
SEM_dk <- as.data.frame(SEM_dk)
colnames(SEM_dk) <- c("sem")
SEM_dk$estimator <- rownames(SEM_dk)

#merge
sum_dk <- merge(means_dk, sd_dk, by.y = "estimator")
all_sum_dk <- merge(sum_dk, SEM_dk, by.y = "estimator")

#separate estimator from threshold
all_sum_dk <- all_sum_dk %>% separate(estimator, into = c('estimator', 'threshold'), sep = -3)
```

## Get summary stats for ln Pr(X|K)) ##

```{r}
#for LnK
#get the means
means_lnk <- as.data.frame(colMeans(lnk_diff))
colnames(means_lnk) <- c("mean")
means_lnk$estimator <- rownames(means_lnk)

#get the sd
sd_lnk <-sapply(lnk_diff, sd)
sd_lnk <- as.data.frame(sd_lnk)
colnames(sd_lnk) <- c("sd")
sd_lnk$estimator <- rownames(sd_lnk)

#get SEM
SEM_lnk <- sapply(lnk_diff, std.error)
SEM_lnk <- as.data.frame(SEM_lnk)
colnames(SEM_lnk) <- c("sem")
SEM_lnk$estimator <- rownames(SEM_lnk)

#merge
sum_lnk <- merge(means_lnk, sd_lnk, by.y = "estimator")
all_sum_lnk <- merge(sum_lnk, SEM_lnk, by.y = "estimator")

#separate estimator from threshold
all_sum_lnk <- all_sum_lnk %>% separate(estimator, into = c('estimator', 'threshold'), sep = -3)
```

## calculate proportion agreement ##
```{r}
#for deltaK
dk_num_0 <- as.data.frame(rowSums(dk_diff == 0))
colnames(dk_num_0) <- c("count")
dk_num_0$prop_agree <- dk_num_0$count / 16

#for lnK
lnk_num_0 <- as.data.frame(rowSums(lnk_diff == 0))
colnames(lnk_num_0) <- c("count")
lnk_num_0$prop_agree <- lnk_num_0$count / 16
```


## Now create dataframe of sample evenness score with proportion agreement ##

```{r}
setwd("~/")
even_propagree <- read.csv(file = "final_prop_even_weighted.csv", header = T)

## remove NAs
even_propagree <- na.omit(even_propagree)

## get the weights
w <- even_propagree$n 
w <- na.omit(w)

# get proportion agreement with ln Pr(X|K))
even_propagree$prop_agree_lnk <- lnk_num_0$prop_agree

```


# broad section #
## Loop to read in each dataset ##

```{r}
setwd("~/broad/all_estimate_files") 

ldfn <- list() 
listcsvn <- dir(pattern = "*.csv") 
for (k in 1:length(listcsvn)){
 ldfn[[k]] <- read.csv(file = listcsvn[k], check.names = F, row.names = 1, header = T)
}
names(ldfn) <- gsub(".csv","",
                       dir(pattern = "*.csv"),
                       fixed = TRUE)
names(ldfn) <- gsub("Results_Estimators_","", names(ldfn), fixed = TRUE)
names(ldfn) <- gsub("_run","", names(ldfn), fixed = TRUE)
```

## process each dataset ##

```{r}
# get only the estimators you want
ldfn_est_only <- lapply(ldfn, function(x) x <- x[-c(3:15), ])

# create a new column with k values
ldfn_k_vals <- lapply(ldfn_est_only, function(x) cbind(x, k_val = colnames(x)[apply(x,1,which.max)]))

#keep only the K values
ldfn_k_vals_only <- lapply(ldfn_k_vals, function(x) x[c('k_val')])

#transpose each
t_ldfn_k_vals_only <- lapply(ldfn_k_vals_only, function(x) as.data.frame(t(x)))

#convert to one big dataframe
one_dfn <- do.call(rbind, t_ldfn_k_vals_only)

#make only numeric
one_dfn[] <- lapply(one_dfn, gsub, pattern= "K=", replacement = "")
one_dfn_num <- as.data.frame(sapply(one_dfn, as.numeric))
rownames(one_dfn_num) <- rownames(one_dfn)
```

## get differences from deltaK and Lnk ##

```{r}
#for deltaK
dk_diffn <- one_dfn_num[,c(1,3:ncol(one_dfn_num))]
dk_diffn[2:ncol(dk_diffn)] <- dk_diffn[2:ncol(dk_diffn)]-dk_diffn[,1]
dk_diffn <- dk_diffn[,2:ncol(dk_diffn)]

#for PP
lnk_diffn <- one_dfn_num[,2:ncol(one_dfn_num)]
lnk_diffn[2:ncol(lnk_diffn)] <- lnk_diffn[2:ncol(lnk_diffn)]-lnk_diffn[,1]
lnk_diffn <- lnk_diffn[,2:ncol(lnk_diffn)]
```


## get summary stats for DeltaK ##

```{r}
#get the means
means_dkn <- as.data.frame(colMeans(dk_diffn))
colnames(means_dkn) <- c("mean")
means_dkn$estimator <- rownames(means_dkn)

#get the sd
sd_dkn <-sapply(dk_diffn, sd)
sd_dkn <- as.data.frame(sd_dkn)
colnames(sd_dkn) <- c("sd")
sd_dkn$estimator <- rownames(sd_dkn)

#get SEM
SEM_dkn <- sapply(dk_diffn, std.error)
SEM_dkn <- as.data.frame(SEM_dkn)
colnames(SEM_dkn) <- c("sem")
SEM_dkn$estimator <- rownames(SEM_dkn)

#merge
sum_dkn <- merge(means_dkn, sd_dkn, by.y = "estimator")
all_sum_dkn <- merge(sum_dkn, SEM_dkn, by.y = "estimator")

#separate estimator from threshold
all_sum_dkn <- all_sum_dkn %>% separate(estimator, into = c('estimator', 'threshold'), sep = -3)
```

## Get summary stats for ln Pr(X|K)) ##

```{r}
#for LnK
#get the means
means_lnkn <- as.data.frame(colMeans(lnk_diffn))
colnames(means_lnkn) <- c("mean")
means_lnkn$estimator <- rownames(means_lnkn)

#get the sd
sd_lnkn <-sapply(lnk_diffn, sd)
sd_lnkn <- as.data.frame(sd_lnkn)
colnames(sd_lnkn) <- c("sd")
sd_lnkn$estimator <- rownames(sd_lnkn)

#get SEM
SEM_lnkn <- sapply(lnk_diffn, std.error)
SEM_lnkn <- as.data.frame(SEM_lnkn)
colnames(SEM_lnkn) <- c("sem")
SEM_lnkn$estimator <- rownames(SEM_lnkn)

#merge
sum_lnkn <- merge(means_lnkn, sd_lnkn, by.y = "estimator")
all_sum_lnkn <- merge(sum_lnkn, SEM_lnkn, by.y = "estimator")

#separate estimator from threshold
all_sum_lnkn <- all_sum_lnkn %>% separate(estimator, into = c('estimator', 'threshold'), sep = -3)
```

## calculate proportion agreement ##
```{r}
#for deltaK
dkn_num_0 <- as.data.frame(rowSums(dk_diffn == 0))
colnames(dkn_num_0) <- c("count")
dkn_num_0$prop_agree <- dkn_num_0$count / 16

#for ln Pr(X|K))
lnkn_num_0 <- as.data.frame(rowSums(lnk_diffn == 0))
colnames(lnkn_num_0) <- c("count")
lnkn_num_0$prop_agree <- lnkn_num_0$count / 16
```

## Now calculate sample evenness ##

```{r}
# read in the files
setwd("~/broad/pop_files")
pops <- list() 
listtxt <- dir(pattern = "*.txt") 
for (k in 1:length(listcsvn)){
 pops[[k]] <- read.table(file = listtxt[k], check.names = F, header = F)
}
names(pops) <- gsub(".txt","",
                       dir(pattern = "*.txt"),
                       fixed = TRUE)
names(pops) <- sub("\\_.*","", names(pops))

# count how many samples for each location for each dataset
pops_only <- lapply(pops, function(x) x <- table(x[,2]))

# convert to dataframe
pops_df <- lapply(pops_only, function (x) x <- as.data.frame(x))

# sum total individuals for each dataset
sums <- lapply(pops_df, transform, totals = sum(Freq))

# divide each count by total
per_pop <- lapply(sums, transform, proportion = Freq / totals)

# take the Ln of per pop
logs_perpop <- lapply(per_pop, transform, logs_pop = log(proportion))

# multiply Ln per pop by per pop
logs_mult <- lapply(logs_perpop, transform, ShanD = proportion * logs_pop)

# sum Diversity index
ShanD_tot <- lapply(logs_mult, transform, tot_shanD =-1 * sum(ShanD))

# calculate total # pops
pop_totals <- lapply(ShanD_tot, function(x) transform(x,num_pops =c(nrow(x))))

# calculate Ln(S)
ln_s <- lapply(pop_totals, transform, lns =log(num_pops))

# calculate evenness score
evennessn <- lapply(ln_s, transform, even = tot_shanD / lns )
```


## create a new dataframe of evenness score and proportion agreement ##
```{r}
# get the weights
wn <- unlist(lapply(evennessn,function(x) x[1,3]))
wn <- as.data.frame(wn)
wn <- wn[,1]

# get evenness score
even_score <- unlist(lapply(evennessn,function(x) x[1,10]))
even_score <- as.data.frame(even_score)

# get proportion agreement with Dk
even_score$prop_agree_dk <- dkn_num_0$prop_agree
even_propagreeN <- even_score

# get proportion agreement with ln Pr(X|K))
even_propagreeN$prop_agree_lnk <- lnkn_num_0$prop_agree
```

# Finalize Figures: combine plots from focused and broad #

## Figure 1: histogram

```{r}
#for deltaK focused
h_dkc <-ggplot(dk_num_0, aes(x=prop_agree)) + 
  geom_histogram(binwidth = 0.2,color="black", fill="grey")+theme_bw()+xlab("Proportion Agreement")

#for LnK focused
h_lnkc <-ggplot(lnk_num_0, aes(x=prop_agree)) + 
  geom_histogram(binwidth = 0.2,color="black", fill="grey")+theme_bw()+xlab("Proportion Agreement")

#for deltaK broad
h_dkn <-ggplot(dkn_num_0, aes(x=prop_agree)) + 
  geom_histogram(binwidth = 0.2,color="black", fill="grey")+theme_bw()+xlab("Proportion Agreement")

#for LnK broad
h_lnkn <-ggplot(lnkn_num_0, aes(x=prop_agree)) + 
  geom_histogram(binwidth = 0.2,color="black", fill="grey")+theme_bw()+xlab("Proportion Agreement")

plot_grid(h_dkc, h_lnkc, h_dkn, h_lnkn, labels = "AUTO")
```

## Figure 2: difference bar plot

```{r}
#for DeltaK focused
pdkc <- ggplot(all_sum_dk, aes(x=threshold, y=mean, fill=estimator)) +
  geom_bar_pattern(position=position_dodge(), stat="identity", colour='black', mapping=aes(pattern=estimator), pattern = c("none", "none", "none", "none", "stripe", "stripe", "stripe", "stripe", "circle", "circle", "circle", "circle", "none", "none", "none", "none")) + scale_fill_grey() +
  guides(fill = guide_legend(override.aes = 
                               list(
                                 pattern = c("none", "stripe", "circle", "none")))) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=0.2,position=position_dodge(0.9))+theme_bw()+xlab("Threshold") + ylab("Mean Difference")

#for LnK focused
plnkc <- ggplot(all_sum_lnk, aes(x=threshold, y=mean, fill=estimator)) +
  geom_bar_pattern(position=position_dodge(), stat="identity", colour='black', mapping=aes(pattern=estimator), pattern = c("none", "none", "none", "none", "stripe", "stripe", "stripe", "stripe", "circle", "circle", "circle", "circle", "none", "none", "none", "none")) + scale_fill_grey() +
  guides(fill = guide_legend(override.aes = 
                               list(
                                 pattern = c("none", "stripe", "circle", "none")))) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=0.2,position=position_dodge(0.9))+theme_bw()+xlab("Threshold") + ylab("Mean Difference")

#for DeltaK non focused
pdkn <- ggplot(all_sum_dkn, aes(x=threshold, y=mean, fill=estimator)) +
  geom_bar_pattern(position=position_dodge(), stat="identity", colour='black', mapping=aes(pattern=estimator), pattern = c("none", "none", "none", "none", "stripe", "stripe", "stripe", "stripe", "circle", "circle", "circle", "circle", "none", "none", "none", "none")) + scale_fill_grey() +
  guides(fill = guide_legend(override.aes = 
                               list(
                                 pattern = c("none", "stripe", "circle", "none")))) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=0.2,position=position_dodge(0.9))+theme_bw()+xlab("Threshold") + ylab("Mean Difference")

#for LnK non focused
plnkn <- ggplot(all_sum_lnkn, aes(x=threshold, y=mean, fill=estimator)) +
  geom_bar_pattern(position=position_dodge(), stat="identity", colour='black', mapping=aes(pattern=estimator), pattern = c("none", "none", "none", "none", "stripe", "stripe", "stripe", "stripe", "circle", "circle", "circle", "circle", "none", "none", "none", "none")) + scale_fill_grey() +
  guides(fill = guide_legend(override.aes = 
                               list(
                                 pattern = c("none", "stripe", "circle", "none")))) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=0.2,position=position_dodge(0.9))+theme_bw()+xlab("Threshold") + ylab("Mean Difference")

plot_grid(pdkc, plnkc, pdkn, plnkn, labels = "AUTO")

```

## Figure 3: threshold trend

```{r}
#melt the dataframes of differences from deltaK
#coral
dk_diff2 <- dk_diff
dk_diff2$dataset <- rownames(dk_diff2)
m_dk_diff2 <- melt(dk_diff2)
#noncoral
dk_diffn2 <- dk_diffn
dk_diffn2$dataset <- rownames(dk_diffn2)
m_dk_diffn2 <- melt(dk_diffn2)

#separate estimator from threshold
#coral
m_sep_dk_diff2 <- m_dk_diff2 %>% separate(variable, into = c('estimator', 'threshold'), sep = -3)
#noncoral
m_sep_dk_diffn2 <- m_dk_diffn2 %>% separate(variable, into = c('estimator', 'threshold'), sep = -3)

#combine estimator name and dataset into new column
#coral
m_sep_dk_diff2$d_e <- paste(m_sep_dk_diff2$dataset, m_sep_dk_diff2$estimator, sep = "_")
#noncoral
m_sep_dk_diffn2$d_e <- paste(m_sep_dk_diffn2$dataset, m_sep_dk_diffn2$estimator, sep = "_")

#give combination a unique ID
#coral
m_dk_diff_id <- m_sep_dk_diff2 %>% group_by(d_e) %>% mutate(id=cur_group_id())
#noncoral
m_dk_diffn_id <- m_sep_dk_diffn2 %>% group_by(d_e) %>% mutate(id=cur_group_id())


#select datasets from each category (broad and focused) with portion of date/timecode as seed:
set.seed(2520)
datasets_coral <- sample(1:104, 2)
datasets_noncoral <- sample(1:61, 2)

selected_coral_thresh <- subset(m_dk_diff_id, id %in% datasets_coral)
selected_noncoral_thresh <- subset(m_dk_diffn_id, id %in% datasets_noncoral)

#add in column to say whether it is broad (noncoral) or focused (coral)
selected_coral_thresh$Category <- c("focused")
selected_noncoral_thresh$Category <- c("broad")

#combine the two
both_selected_thresh <- rbind(selected_coral_thresh, selected_noncoral_thresh)

#plot it
g <- ggplot(both_selected_thresh, aes(x = factor(threshold), y = value, linetype = d_e, group = d_e, shape = Category)) + geom_line() +
  geom_point(size = 2) + theme_bw() + xlab("Threshold") + ylab("Difference from ΔK") + labs(linetype='Dataset & Estimator') 

g

```

## Figure 4: linear regression

```{r}
par(mfrow=c(2,2))
#dk focused
plot(prop_agree~even, data = even_propagree, xlab="Evenness Score", ylab="Proportion Agreement", main="A")
lmdk <- lm(prop_agree~even, data = even_propagree, weights=w)
abline(lmdk, col ="black", lty="dashed")
#lnk focused
plot(prop_agree_lnk~even, data = even_propagree, xlab="Evenness Score", ylab="Proportion Agreement", main="B")
lmln <- lm(prop_agree_lnk~even, data = even_propagree, weights=w)
abline(lmln, col ="black", lty="dashed")
#dk broad
plot(prop_agree_dk~even_score, data = even_propagreeN, xlab="Evenness Score", ylab="Proportion Agreement", main="C")
lmdkn <- lm(prop_agree_dk~even_score, data = even_propagreeN, weights=wn)
abline(lmdkn, col ="black", lty="dashed")
#lnk broad
plot(prop_agree_lnk~even_score, data = even_propagreeN, xlab="Evenness Score", ylab="Proportion Agreement", main="D")
lmlnn <- lm(prop_agree_lnk~even_score, data = even_propagreeN, weights=wn)
abline(lmlnn, col ="black", lty="dashed")
```


# AMOVA #

### First find datasets where Lnk and Dk disagree fully with alt ests and randomly select two

```{r}
# set the seed as year
set.seed(2021)
#### broad Datasets
all_props_nc <- cbind(dkn_num_0, lnkn_num_0)
colnames(all_props_nc) <- c("count_dk", "prop_agree_dk", "count_lnk", "prop_agree_lnk")

k_est_disagree_nc <- all_props_nc %>% filter(count_dk == "0" & count_lnk == "0")
selected_nc <- k_est_disagree_nc[sample(nrow(k_est_disagree_nc), 2), ]

#### focused Datasets
all_props <- cbind(dk_num_0, lnk_num_0)
colnames(all_props) <- c("count_dk", "prop_agree_dk", "count_lnk", "prop_agree_lnk")

k_est_disagree <- all_props %>% filter(count_dk == "0" & count_lnk == "0")
selected_corals <- k_est_disagree[sample(nrow(k_est_disagree), 2), ]
```

### Get unique K values to test for both datasets
```{r}
#broad datasets
kim_uniq_k <- unique(as.data.frame(t(one_dfn_num))[c("kim")])
perez_uniq_k <- unique(as.data.frame(t(one_dfn_num))[c("perez")])
kim_uniq_k
perez_uniq_k

#focused datasets
baums_uniq_k <- unique(as.data.frame(t(one_df_num))[c("baums2010_mf")])
rippe_uniq_k <- unique(as.data.frame(t(one_df_num))[c("rippe")])
baums_uniq_k
rippe_uniq_k
```


#### Read in the data for the clump files

```{r}


#################### Kim, K=2,5-8
kim_2_clumpp <- read.table("~/broad/clump_zip/clump_results/1614710948/1614710948/K=2/CLUMPP.files/ClumppIndFile.output")
kim_5_clumpp <- read.table("~/broad/clump_zip/clump_results/1614710948/1614710948/K=5/CLUMPP.files/ClumppIndFile.output")
kim_6_clumpp <- read.table("~/broad/clump_zip/clump_results/1614710948/1614710948/K=6/CLUMPP.files/ClumppIndFile.output")
kim_7_clumpp <- read.table("~/broad/clump_zip/clump_results/1614710948/1614710948/K=7/CLUMPP.files/ClumppIndFile.output")
kim_8_clumpp <- read.table("~/broad/clump_zip/clump_results/1614710948/1614710948/K=8/CLUMPP.files/ClumppIndFile.output")

#################### Perez, K=2,7,12
perez_2_clumpp <- read.table("~/broad/clump_zip/clump_results/1614711525/1614711525/K=2/CLUMPP.files/ClumppIndFile.output")
perez_7_clumpp <- read.table("~/broad/clump_zip/clump_results/1614711525/1614711525/K=7/CLUMPP.files/ClumppIndFile.output")
perez_12_clumpp <- read.table("~/broad/clump_zip/clump_results/1614711525/1614711525/K=12/CLUMPP.files/ClumppIndFile.output")

###### focused Datasets ######

#################### Baums, K=1-3
baums10mf_2_clumpp <- read.table("~/focused/clump_zip/clump_results/1614699356/1614699356/K=2/CLUMPP.files/ClumppIndFile.output")
baums10mf_3_clumpp <- read.table("~/focused/clump_zip/clump_results/1614699356/1614699356/K=3/CLUMPP.files/ClumppIndFile.output")

#################### Rippe, K=2-5,10
rippe_2_clumpp <- read.table("~/focused/clump_zip/clump_results/1614701985/1614701985/K=2/CLUMPP.files/ClumppIndFile.output")
rippe_3_clumpp <- read.table("~/focused/clump_zip/clump_results/1614701985/1614701985/K=3/CLUMPP.files/ClumppIndFile.output")
rippe_4_clumpp <- read.table("~/focused/clump_zip/clump_results/1614701985/1614701985/K=4/CLUMPP.files/ClumppIndFile.output")
rippe_5_clumpp <- read.table("~/focused/clump_zip/clump_results/1614701985/1614701985/K=5/CLUMPP.files/ClumppIndFile.output")
rippe_10_clumpp <- read.table("~/focused/clump_zip/clump_results/1614701985/1614701985/K=10/CLUMPP.files/ClumppIndFile.output")

```

### Assign individuals to populations
```{r}
##### broad Datasets
### Kim
kim_2_clumpp <- kim_2_clumpp[, c(6:ncol(kim_2_clumpp))]
colnames(kim_2_clumpp) <- c(seq(1,2))
kim_2_clumpp$Pop <- colnames(kim_2_clumpp)[apply(kim_2_clumpp,1,which.max)]

kim_5_clumpp <- kim_5_clumpp[, c(6:ncol(kim_5_clumpp))]
colnames(kim_5_clumpp) <- c(seq(1,5))
kim_5_clumpp$Pop <- colnames(kim_5_clumpp)[apply(kim_5_clumpp,1,which.max)]

kim_6_clumpp <- kim_6_clumpp[, c(6:ncol(kim_6_clumpp))]
colnames(kim_6_clumpp) <- c(seq(1,6))
kim_6_clumpp$Pop <- colnames(kim_6_clumpp)[apply(kim_6_clumpp,1,which.max)]

kim_7_clumpp <- kim_7_clumpp[, c(6:ncol(kim_7_clumpp))]
colnames(kim_7_clumpp) <- c(seq(1,7))
kim_7_clumpp$Pop <- colnames(kim_7_clumpp)[apply(kim_7_clumpp,1,which.max)]

kim_8_clumpp <- kim_8_clumpp[, c(6:ncol(kim_8_clumpp))]
colnames(kim_8_clumpp) <- c(seq(1,8))
kim_8_clumpp$Pop <- colnames(kim_8_clumpp)[apply(kim_8_clumpp,1,which.max)]

### Perez
perez_2_clumpp <- perez_2_clumpp[, c(6:ncol(perez_2_clumpp))]
colnames(perez_2_clumpp) <- c(seq(1,2))
perez_2_clumpp$Pop <- colnames(perez_2_clumpp)[apply(perez_2_clumpp,1,which.max)]

perez_7_clumpp <- perez_7_clumpp[, c(6:ncol(perez_7_clumpp))]
colnames(perez_7_clumpp) <- c(seq(1,7))
perez_7_clumpp$Pop <- colnames(perez_7_clumpp)[apply(perez_7_clumpp,1,which.max)]

perez_12_clumpp <- perez_12_clumpp[, c(6:ncol(perez_12_clumpp))]
colnames(perez_12_clumpp) <- c(seq(1,12))
perez_12_clumpp$Pop <- colnames(perez_12_clumpp)[apply(perez_12_clumpp,1,which.max)]

##### focused Datasets

### Baums
baums10mf_2_clumpp <- baums10mf_2_clumpp[, c(6:ncol(baums10mf_2_clumpp))]
colnames(baums10mf_2_clumpp) <- c(seq(1,2))
baums10mf_2_clumpp$Pop <- colnames(baums10mf_2_clumpp)[apply(baums10mf_2_clumpp,1,which.max)]

baums10mf_3_clumpp <- baums10mf_3_clumpp[, c(6:ncol(baums10mf_3_clumpp))]
colnames(baums10mf_3_clumpp) <- c(seq(1,3))
baums10mf_3_clumpp$Pop <- colnames(baums10mf_3_clumpp)[apply(baums10mf_3_clumpp,1,which.max)]

### Rippe
rippe_2_clumpp <- rippe_2_clumpp[, c(6:ncol(rippe_2_clumpp))]
colnames(rippe_2_clumpp) <- c(seq(1,2))
rippe_2_clumpp$Pop <- colnames(rippe_2_clumpp)[apply(rippe_2_clumpp,1,which.max)]

rippe_3_clumpp <- rippe_3_clumpp[, c(6:ncol(rippe_3_clumpp))]
colnames(rippe_3_clumpp) <- c(seq(1,3))
rippe_3_clumpp$Pop <- colnames(rippe_3_clumpp)[apply(rippe_3_clumpp,1,which.max)]

rippe_4_clumpp <- rippe_4_clumpp[, c(6:ncol(rippe_4_clumpp))]
colnames(rippe_4_clumpp) <- c(seq(1,4))
rippe_4_clumpp$Pop <- colnames(rippe_4_clumpp)[apply(rippe_4_clumpp,1,which.max)]

rippe_5_clumpp <- rippe_5_clumpp[, c(6:ncol(rippe_5_clumpp))]
colnames(rippe_5_clumpp) <- c(seq(1,5))
rippe_5_clumpp$Pop <- colnames(rippe_5_clumpp)[apply(rippe_5_clumpp,1,which.max)]

rippe_10_clumpp <- rippe_10_clumpp[, c(6:ncol(rippe_10_clumpp))]
colnames(rippe_10_clumpp) <- c(seq(1,10))
rippe_10_clumpp$Pop <- colnames(rippe_10_clumpp)[apply(rippe_10_clumpp,1,which.max)]

```

### Read in the genotype files
```{r}
#must rename the structure input files to end in .stru
#if a pop column (eg. from sampling sites) does already exist, designate it as "other" to retain the info

### broad Datasets
#Kim
kim_geno2 <- read.structure("~/broad/kim/kim/kim_2017_fixed.stru", n.ind = 320, n.loc = 8, onerowperind = TRUE, col.lab = 1, col.pop = 0, col.others = 2, NA.char =-9, ask = FALSE, row.marknames = 0)

kim_geno5 <- kim_geno2
kim_geno6 <- kim_geno2
kim_geno7 <- kim_geno2
kim_geno8 <- kim_geno2

#Perez
perez_geno2 <- read.structure("~/broad/perez/perez/perez_2014_fixed2.stru", n.ind = 330, n.loc = 9, onerowperind = TRUE, col.lab = 1, col.pop = 0, col.others = 2, NA.char =-9, ask = FALSE, row.marknames = 0)

perez_geno7 <- perez_geno2

# focused datasets

#Baums
baums10_geno2 <- read.structure("~/focused/baums_2010_mfav/baums_mfav.stru", n.ind = 182, n.loc = 5, onerowperind = TRUE, col.lab = 1, col.pop = 0, col.others = 2:3, NA.char = -9, ask = FALSE)

baums10_geno3 <- baums10_geno2

# Rippe
rippe_geno2 <- read.structure("~/focused/rippe/Rippe2017_fixed.stru", n.ind = 369, n.loc = 9, onerowperind = TRUE, col.lab = 1, col.pop = 0, col.others = 2:3, NA.char = -9, ask = FALSE, row.marknames = 1)

rippe_geno3 <- rippe_geno2
rippe_geno4 <- rippe_geno2
rippe_geno5 <- rippe_geno2
rippe_geno10 <- rippe_geno2
```

### Add in the strata and pop information
```{r}
### broad Datasets

## Kim 
strata(kim_geno2) <- kim_2_clumpp[c("Pop")]
setPop(kim_geno2) <- ~Pop
kim2_genclone <- as.genclone(kim_geno2)

strata(kim_geno5) <- kim_5_clumpp[c("Pop")]
setPop(kim_geno5) <- ~Pop
kim5_genclone <- as.genclone(kim_geno5)

strata(kim_geno6) <- kim_6_clumpp[c("Pop")]
setPop(kim_geno6) <- ~Pop
kim6_genclone <- as.genclone(kim_geno6)

strata(kim_geno7) <- kim_7_clumpp[c("Pop")]
setPop(kim_geno7) <- ~Pop
kim7_genclone <- as.genclone(kim_geno7)

strata(kim_geno8) <- kim_8_clumpp[c("Pop")]
setPop(kim_geno8) <- ~Pop
kim8_genclone <- as.genclone(kim_geno8)

## Perez
strata(perez_geno2) <- perez_2_clumpp[c("Pop")]
setPop(perez_geno2) <- ~Pop
perez2_genclone <- as.genclone(perez_geno2)

strata(perez_geno7) <- perez_7_clumpp[c("Pop")]
setPop(perez_geno7) <- ~Pop
perez7_genclone <- as.genclone(perez_geno7)

### focused datasets

# Baums
strata(baums10_geno2) <- baums10mf_2_clumpp[c("Pop")]
setPop(baums10_geno2) <- ~Pop
baums2_genclone <- as.genclone(baums10_geno2)

strata(baums10_geno3) <- baums10mf_3_clumpp[c("Pop")]
setPop(baums10_geno3) <- ~Pop
baums3_genclone <- as.genclone(baums10_geno3)

# Rippe
strata(rippe_geno2) <- rippe_2_clumpp[c("Pop")]
setPop(rippe_geno2) <- ~Pop
rippe2_genclone <- as.genclone(rippe_geno2)

strata(rippe_geno3) <- rippe_3_clumpp[c("Pop")]
setPop(rippe_geno3) <- ~Pop
rippe3_genclone <- as.genclone(rippe_geno3)

strata(rippe_geno4) <- rippe_4_clumpp[c("Pop")]
setPop(rippe_geno4) <- ~Pop
rippe4_genclone <- as.genclone(rippe_geno4)

strata(rippe_geno5) <- rippe_5_clumpp[c("Pop")]
setPop(rippe_geno5) <- ~Pop
rippe5_genclone <- as.genclone(rippe_geno5)

strata(rippe_geno10) <- rippe_10_clumpp[c("Pop")]
setPop(rippe_geno10) <- ~Pop
rippe10_genclone <- as.genclone(rippe_geno10)
```

### Run AMOVA
```{r}
# broad datasets
# Kim
kim2_amova <- poppr.amova(kim2_genclone, ~Pop)
kim5_amova <- poppr.amova(kim5_genclone, ~Pop)
kim6_amova <- poppr.amova(kim6_genclone, ~Pop)
kim7_amova <- poppr.amova(kim7_genclone, ~Pop)
kim8_amova <- poppr.amova(kim8_genclone, ~Pop)

# Perez
perez2_amova <- poppr.amova(perez2_genclone, ~Pop)
perez7_amova <- poppr.amova(perez7_genclone, ~Pop)

# focused datasets
# Baums
baums2_amova <- poppr.amova(baums2_genclone, ~Pop)
baums3_amova <- poppr.amova(baums3_genclone, ~Pop)

# Rippe
rippe2_amova <- poppr.amova(rippe2_genclone, ~Pop)
rippe3_amova <- poppr.amova(rippe3_genclone, ~Pop)
rippe4_amova <- poppr.amova(rippe4_genclone, ~Pop)
rippe5_amova <- poppr.amova(rippe5_genclone, ~Pop)
rippe10_amova <- poppr.amova(rippe10_genclone, ~Pop)
```

# Check the results
```{r}
# broad datasets
# Kim
kim2_amova
kim5_amova
kim6_amova
kim7_amova
kim8_amova

# Perez
perez2_amova 
perez7_amova 

# focused datasets 
# Baums
baums2_amova
baums3_amova

# Rippe
rippe2_amova
rippe3_amova
rippe4_amova
rippe5_amova
rippe10_amova
```




### Run significance test
this will take a long time
```{r}
#set seed, taken from poppr tutorial
set.seed(1999)
# broad datasets
# Kim
kim2_test <- randtest(kim2_amova, nrepet = 999)
kim5_test <- randtest(kim5_amova, nrepet = 999)
kim6_test <- randtest(kim6_amova, nrepet = 999)
kim7_test <- randtest(kim7_amova, nrepet = 999)
kim8_test <- randtest(kim8_amova, nrepet = 999)

# Perez
perez2_test <- randtest(perez2_amova, nrepet = 999)
perez7_test <- randtest(perez7_amova, nrepet = 999)

# focused datasets
# Baums
baums2_test <- randtest(baums2_amova, nrepet = 999)
baums3_test <- randtest(baums3_amova, nrepet = 999)

# Rippe
rippe2_test <- randtest(rippe2_amova, nrepet = 999)
rippe3_test <- randtest(rippe3_amova, nrepet = 999)
rippe4_test <- randtest(rippe4_amova, nrepet = 999)
rippe5_test <- randtest(rippe5_amova, nrepet = 999)
rippe10_test <- randtest(rippe10_amova, nrepet = 999)
```

# Check the results
```{r}
# broad datasets
# Kim
kim2_test
kim5_test
kim6_test
kim7_test
kim8_test

# Perez
perez2_test
perez7_test

# focused datasets
# Baums
baums2_test
baums3_test

# Rippe
rippe2_test
rippe3_test
rippe4_test
rippe5_test
rippe10_test
```


# write out the results
```{r}
# broad
# Kim
write.table(kim2_amova$componentsofcovariance, sep = ",", file = "kim2_amova.csv")
write.table(kim5_amova$componentsofcovariance, sep = ",", file = "kim5_amova.csv")
write.table(kim6_amova$componentsofcovariance, sep = ",", file = "kim6_amova.csv")
write.table(kim7_amova$componentsofcovariance, sep = ",", file = "kim7_amova.csv")
write.table(kim8_amova$componentsofcovariance, sep = ",", file = "kim8_amova.csv")

# Perez
write.table(perez2_amova$componentsofcovariance, sep = ",", file = "perez2_amova.csv")
write.table(perez7_amova$componentsofcovariance, sep = ",", file = "perez7_amova.csv")

# focused
# Baums
write.table(baums2_amova$componentsofcovariance, sep = ",", file = "baums2_amova.csv")
write.table(baums3_amova$componentsofcovariance, sep = ",", file = "baums3_amova.csv")

# Rippe
write.table(rippe2_amova$componentsofcovariance, sep = ",", file = "rippe2_amova.csv")
write.table(rippe3_amova$componentsofcovariance, sep = ",", file = "rippe3_amova.csv")
write.table(rippe4_amova$componentsofcovariance, sep = ",", file = "rippe4_amova.csv")
write.table(rippe5_amova$componentsofcovariance, sep = ",", file = "rippe5_amova.csv")
write.table(rippe10_amova$componentsofcovariance, sep = ",", file = "rippe10_amova.csv")
```











































